### 2022-12-09 dissertation/appendix/symbols.tex
✨ (symbols): Chapter 5 done

\begin{description}
	\item [\parbox{2cm}{$\alpha_{0}$}]
	\item [\parbox{2cm}{$\alpha_{1}$}]
	\item [\parbox{2cm}{$\alpha_{k}$}]
	\item [\parbox{2cm}{$\alpha_{K}$}]
	\item [\parbox{2cm}{$\alpha$}]
	\item [\parbox{2cm}{$\bar{A}$}]
	\item [\parbox{2cm}{$\beta'$ }]
	\item [\parbox{2cm}{$\beta$}]
	\item [\parbox{2cm}{$Bin$}]
	\item [\parbox{2cm}{$\boldsymbol{\alpha'}$}]
	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
	\item [\parbox{2cm}{$\boldsymbol{\mathcal{D}}$}]
	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
	\item [\parbox{2cm}{$\boldsymbol{N}$}]
	\item [\parbox{2cm}{$\boldsymbol{x_{1}}$}]
	\item [\parbox{2cm}{$\boldsymbol{x_{i}}$}]
	\item [\parbox{2cm}{$\boldsymbol{x_{I}}$}]
	\item [\parbox{2cm}{$\boldsymbol{x}$}]
	\item [\parbox{2cm}{$\boldsymbol{X}$}]
	\item [\parbox{2cm}{$\boldsymbol{Y}$}]
	\item [\parbox{2cm}{$\emptyset$}]
	\item [\parbox{2cm}{$\Gamma'(n)$}]
	\item [\parbox{2cm}{$\Gamma(n)$}]
	\item [\parbox{2cm}{$\Gamma$}]
	\item [\parbox{2cm}{$\mathbb{R}$}]
	\item [\parbox{2cm}{$\mathbbm{1}$}]
	\item [\parbox{2cm}{$\mathcal{A}$}]
	\item [\parbox{2cm}{$\mathcal{L}$}]
	\item [\parbox{2cm}{$\overset{\text{iid}}{\sim}$}]
	\item [\parbox{2cm}{$\psi$}]
	\item [\parbox{2cm}{$\theta_{1}$}]
	\item [\parbox{2cm}{$\theta_{k}$}]
	\item [\parbox{2cm}{$\theta_{K}$}]
	\item [\parbox{2cm}{$\theta$}]
	\item [\parbox{2cm}{$A$}]
	\item [\parbox{2cm}{$B_{1}$}]
	\item [\parbox{2cm}{$B_{2}$}]
	\item [\parbox{2cm}{$B_{i}$}]
	\item [\parbox{2cm}{$B_{j}$}]
	\item [\parbox{2cm}{$B_{K}$}]
	\item [\parbox{2cm}{$B(\boldsymbol{\alpha})$}]
	\item [\parbox{2cm}{$B$}]
	\item [\parbox{2cm}{$Ber(\theta)$}]
	\item [\parbox{2cm}{$Beta$}]
	\item [\parbox{2cm}{$Bin$}]
	\item [\parbox{2cm}{$c$}]
	\item [\parbox{2cm}{$Cat$}]
	\item [\parbox{2cm}{$d$}]
	\item [\parbox{2cm}{$Dir$}]
	\item [\parbox{2cm}{$dn$}]
	\item [\parbox{2cm}{$E[{x_{k}}]$}]
	\item [\parbox{2cm}{$E[\ln(x_{k})]$}]
	\item [\parbox{2cm}{$E[\ln(x)]$}]
	\item [\parbox{2cm}{$E[x_{k}]$}]
	\item [\parbox{2cm}{$E[x]$}]
	\item [\parbox{2cm}{$f_{Ber}$}]
	\item [\parbox{2cm}{$f_{Beta}$}]
	\item [\parbox{2cm}{$f_{Bin}$}]
	\item [\parbox{2cm}{$f_{Cat}$}]
	\item [\parbox{2cm}{$f_{Dir}$}]
	\item [\parbox{2cm}{$f_{Mul}$}]
	\item [\parbox{2cm}{$f$}]
	\item [\parbox{2cm}{$F$}]
	\item [\parbox{2cm}{$g^{*}$}]
	\item [\parbox{2cm}{$g$}]
	\item [\parbox{2cm}{$i$}]
	\item [\parbox{2cm}{$I$}]
	\item [\parbox{2cm}{$j$}]
	\item [\parbox{2cm}{$K$}]
	\item [\parbox{2cm}{$k$}]
	\item [\parbox{2cm}{$K$}]
	\item [\parbox{2cm}{$M[x_{k}]$}]
	\item [\parbox{2cm}{$M[x]$}]
	\item [\parbox{2cm}{$m$}]
	\item [\parbox{2cm}{$M$}]
	\item [\parbox{2cm}{$Mul$}]
	\item [\parbox{2cm}{$N_{0}$}]
	\item [\parbox{2cm}{$N_{1}$}]
	\item [\parbox{2cm}{$N_{k}$}]
	\item [\parbox{2cm}{$N_{K}$}]
	\item [\parbox{2cm}{$n$}]
	\item [\parbox{2cm}{$N$}]
	\item [\parbox{2cm}{$p$}]
	\item [\parbox{2cm}{$S$}]
	\item [\parbox{2cm}{$v$}]
	\item [\parbox{2cm}{$x_{1}$}]
	\item [\parbox{2cm}{$x_{i,k}$}]
	\item [\parbox{2cm}{$x_{i}$}]
	\item [\parbox{2cm}{$x_{I}$}]
	\item [\parbox{2cm}{$x_{j}$}]
	\item [\parbox{2cm}{$x_{k}$}]
	\item [\parbox{2cm}{$x_{K}$}]
	\item [\parbox{2cm}{$x$}]
	\item [\parbox{2cm}{$y_{1}$}]
	\item [\parbox{2cm}{$Y_{1}$}]
	\item [\parbox{2cm}{$y_{2}$}]
	\item [\parbox{2cm}{$Y_{2}$}]
	\item [\parbox{2cm}{$y_{i}$}]
	\item [\parbox{2cm}{$Y_{i}$}]
	\item [\parbox{2cm}{$y_{n}$}]
	\item [\parbox{2cm}{$Y_{N}$}]
\end{description}

>>>>

	\item [\parbox{2cm}{$A$}] Random event.
	\item [\parbox{2cm}{$P$}] The probability of some event.
	\item [\parbox{2cm}{$N$}] The total number of events observed.
	\item [\parbox{2cm}{$B$}] Random event.
	\item [\parbox{2cm}{$\bar{A}$}] Not observing random event $A$.
	\item [\parbox{2cm}{$B_{1}$}] The first set in the partition $S$.
	\item [\parbox{2cm}{$B_{2}$}] The second set in the partition $S$.
	\item [\parbox{2cm}{$B_{i}$}] The $i$-th set in the partition $S$.
	\item [\parbox{2cm}{$B_{j}$}] The $j$-th set in the partition $S$.
	\item [\parbox{2cm}{$B_{K}$}] The last set in the partition $S$.
	\item [\parbox{2cm}{$S$}] The union of mutually exclusion subsets. Also referred to as the probability simplex.
	\item [\parbox{2cm}{$i$}] Index to track sets in partition $S$. Also used as a general index in random variables in $I$ dimensions.
	\item [\parbox{2cm}{$j$}] Index to track sets in partition $S$. Also used as a general index in random variables in $J$ dimensions.
	\item [\parbox{2cm}{$k$}] Index used to denote class $k$ in $K$ classes. Also used as a general index in random variables in $K$ dimensions.
	\item [\parbox{2cm}{$K$}] The total number of sets in the partition $S$. Also used to denote the number of classes in the Dirichlet probability distribution.
	\item [\parbox{2cm}{$\alpha$}] Shape parameter for the Beta probability distribution. Also used for confidence levels for the statistical tests.
	\item [\parbox{2cm}{$x$}] Random variable used by various probability distributions. Also referred to as a realisation of an event that occurred as a results of a random process $X$.
	\item [\parbox{2cm}{$\beta$}] Shape parameter for the Beta probability distribution.
	\item [\parbox{2cm}{$Beta$}] The Beta probability distribution.
	\item [\parbox{2cm}{$f_{Beta}$}] The \acs{PDF} of the Beta probability distribution.
	\item [\parbox{2cm}{$B(\alpha, \beta)$}] The normalising constant used in the \acs{PDF} of the Beta probability distribution.
	\item [\parbox{2cm}{$\Gamma$}] The Gamma function.
	\item [\parbox{2cm}{$n$}] Input parameter to the Gamma function.
	\item [\parbox{2cm}{$E[x]$}] The expected value of the distribution of $x$.
	\item [\parbox{2cm}{$E[\ln(x)]$}] The expected value of the natural logarithm of $x$.
	\item [\parbox{2cm}{$\psi$}] The logarithmic derivative of the Gamma function, called the Digamma Function.
	\item [\parbox{2cm}{$\Gamma(n)$}] The Gamma function over input $n$.
	\item [\parbox{2cm}{$\Gamma'(n)$}] The first derivative of the Gamma function over input $n$.
	\item [\parbox{2cm}{$M[x]$}] The mode of the distribution of $x$.
	\item [\parbox{2cm}{$\boldsymbol{x}$}] The random variable for various probability distributions in multiple dimensions.
	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}] The concentration parameter vector that parameterises the Dirichlet probability distribution.
	\item [\parbox{2cm}{$\alpha_{1}$}] The first dimension of the concentration parameter $\boldsymbol{\alpha}$.
	\item [\parbox{2cm}{$\alpha_{k}$}] The $k$-th dimension of the concentration parameter $\boldsymbol{\alpha}$.
	\item [\parbox{2cm}{$\alpha_{K}$}] The last dimension of the concentration parameter $\boldsymbol{\alpha}$.
	\item [\parbox{2cm}{$Dir$}] The Dirichlet probability distribution.
	\item [\parbox{2cm}{$f_{Dir}$}] The \acs{PDF} of the Dirichlet probability distribution.
	\item [\parbox{2cm}{$B(\boldsymbol{\alpha})$}] The normalising constant used in the \acs{PDF} of the Dirichlet probability distribution.
	\item [\parbox{2cm}{$\alpha_{0}$}] The sum of all the values in each dimension of the concentration parameter $\boldsymbol{\alpha}$.
	\item [\parbox{2cm}{$x_{1}$}] The first dimension of the random variable. Also used as the first random event.
	\item [\parbox{2cm}{$x_{i}$}] The $i$-th dimension of the random variable. Also used as the $i$-th random event.
	\item [\parbox{2cm}{$x_{j}$}] The $j$-th dimension of the random variable. Also used as the $j$-th random event.
	\item [\parbox{2cm}{$x_{k}$}] The $k$-th dimension of the random variable. Also used as the $k$-th random event.
	\item [\parbox{2cm}{$x_{I}$}] The last dimension of the random variable with $I$ dimensions. Also used as the last random event in $I$ random events.
	\item [\parbox{2cm}{$x_{K}$}] The last dimension of the random variable with $K$ dimensions. Also used as the last random event in $K$ random events.
	\item [\parbox{2cm}{$c$}] Symmetric distribution constant.
	\item [\parbox{2cm}{$E[x_{k}]$}] The expected value of the $k$-th dimension of the random variable.
	\item [\parbox{2cm}{$E[\ln(x_{k})]$}] The expected value of the natural logarithm of the $k$-th dimension of the random variable.
	\item [\parbox{2cm}{$M[x_{k}]$}] The mode of the $k$-th dimension of the random variable.
	\item [\parbox{2cm}{$\theta$}] Success probability for the Bernoulli probability distribution.
	\item [\parbox{2cm}{$Ber$}] The Bernoulli probability distribution.
	\item [\parbox{2cm}{$f_{Ber}$}] The \acs{PMF} for the Bernoulli probability distribution.
	\item [\parbox{2cm}{$Bin$}] The Binomial probability distribution.
	\item [\parbox{2cm}{$f_{Bin}$}] The \acs{PMF} for the Binomial probability distribution.
	\item [\parbox{2cm}{$\boldsymbol{\theta}$}] The probability vector in multiple dimensions used by multiple probability distributions.
	\item [\parbox{2cm}{$\theta_{1}$}] The first dimension of the probability vector $\boldsymbol{\theta}$.
	\item [\parbox{2cm}{$\theta_{k}$}] The $k$-th dimension of the probability vector $\boldsymbol{\theta}$.
	\item [\parbox{2cm}{$\theta_{K}$}] The last dimension of the probability vector $\boldsymbol{\theta}$.
	\item [\parbox{2cm}{$Cat$}] The Categorical probability distribution.
	\item [\parbox{2cm}{$f_{Cat}$}] The \acs{PMF} for the Categorical probability distribution.
	\item [\parbox{2cm}{$\mathbbm{1}$}] Indicator function.
	\item [\parbox{2cm}{$Mul$}] The Multinomial probability distribution.
	\item [\parbox{2cm}{$f_{Mul}$}] The \acs{PMF} for the Multinomial probability distribution.
	\item [\parbox{2cm}{$\boldsymbol{X}$}] Matrix of Bernoulli probability distributions. Also used to represent the outcomes of $I$ independent, identical (iid) random events.
	\item [\parbox{2cm}{$x_{i,k}$}] The $k$-th dimension of the $i$-th random event vector $\boldsymbol{x}$.
	\item [\parbox{2cm}{$N_{k}$}] is a summary variable, denoting the number of times a category $k$ occurs over all trials in $N$.
	\item [\parbox{2cm}{$\boldsymbol{x_{1}}$}] The outcomes of the first random event in $I$ independent, identical (iid) events for $k$ categories.
	\item [\parbox{2cm}{$\boldsymbol{x_{I}}$}] The outcomes of the last random event in $I$ independent, identical (iid) events for $k$ categories.
	\item [\parbox{2cm}{$\boldsymbol{x_{i}}$}] The outcomes of the $i$-th random event in $I$ independent, identical (iid) events for $k$ categories.
	\item [\parbox{2cm}{$\overset{\text{iid}}{\sim}$}] Independent, identical (iid) random events.
	\item [\parbox{2cm}{$\boldsymbol{N}$}] The counts for each occurrence of a category $k$ over $I$ independent, identical (iid) events.
	\item [\parbox{2cm}{$I$}] The total number of independent, identical (iid) random events.
	\item [\parbox{2cm}{$\mathcal{A}(v)$}] Functional form of priors.
	\item [\parbox{2cm}{$\mathbb{R}$}] Real-number space.
	\item [\parbox{2cm}{$\mathcal{L}$}] The likelihood function.
	\item [\parbox{2cm}{$\boldsymbol{\mathcal{D}}$}] All the prior data of $\boldsymbol{X}$
	\item [\parbox{2cm}{$N_{0}$}] Summary variable tracking the number of unsuccessful Boolean outcomes.
	\item [\parbox{2cm}{$N_{1}$}] Summary variable tracking the number of successful Boolean outcomes.
	\item [\parbox{2cm}{$N_{K}$}] Summary variable denoting the number of times category $k$ occurs.
	\item [\parbox{2cm}{$\alpha'$ }] The update form of the prior parameter, $\alpha$, for a Beta probability distribution.
	\item [\parbox{2cm}{$\beta'$ }] The update form of the prior parameter, $\beta$, for a Beta probability distribution.
	\item [\parbox{2cm}{$\boldsymbol{\alpha'}$}] Update form of the prior parameter, $\boldsymbol{\alpha}$, for a Dirichlet probability distribution.
	\item [\parbox{2cm}{$p$}] The statistical $p$-value.
	\item [\parbox{2cm}{$\boldsymbol{Y}$}] A vector of random events.
	\item [\parbox{2cm}{$Y_{1}$}] The first random event in $\boldsymbol{Y}$.
	\item [\parbox{2cm}{$Y_{2}$}] The second random event in $\boldsymbol{Y}$.
	\item [\parbox{2cm}{$Y_{i}$}] The $i$-th random event in $\boldsymbol{Y}$.
	\item [\parbox{2cm}{$Y_{N}$}] The last random event in $\boldsymbol{Y}$ with $N$ events.
	\item [\parbox{2cm}{$y_{1}$}] The realisation of the first random event in $\boldsymbol{Y}$.
	\item [\parbox{2cm}{$y_{2}$}] The realisation of the second random event in $\boldsymbol{Y}$.
	\item [\parbox{2cm}{$y_{i}$}] The realisation of the $i$-th random event in $\boldsymbol{Y}$.
	\item [\parbox{2cm}{$y_{n}$}] The realisation of the $n$-th random event in $\boldsymbol{Y}$ with $N$ events.
	\item [\parbox{2cm}{$g$}] Prior density.
	\item [\parbox{2cm}{$g^{*}$}] Posterior density.
	\item [\parbox{2cm}{$f$}] General symbol used for functions. Used for likelihood functions, \acp{PMF} and \acp{PDF}.
	\item [\parbox{2cm}{$m$}] The marginal density function.
	\item [\parbox{2cm}{$M$}] The symbol used for a male outcome in the mice experiment.
	\item [\parbox{2cm}{$F$}] The symbol used for a female outcome in the mice experiment.
